Estill 2016 reanalysis

### 2023-12-18 figs/ART_estill2016.Rmd
fix anno

top_nat_vs_fh_inc <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval,name="top_nat_vs_fh_inc",
    myann=myann ,beta= beta)

@@

top_nat_vs_fh <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fh",
    myann=myann, beta=beta_flt)

@@

top_nat_vs_fz <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fz",
    myann=myann, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="NAT" | art=="IUI")
groups <- factor(samplesheet$art,levels=c("NAT","IUI"))
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_nat_vs_iui <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_iui",
    myann=myann, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="FH" | art=="FZ")
groups <- factor(samplesheet$art,levels=c("FH","FZ"))
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_fh_vs_fz <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_fh_vs_fz",
    myann=myann, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="NAT" | art=="FH" | art=="FZ")
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
samplesheet$art <- gsub("FH","FX",samplesheet$art)
samplesheet$art <- gsub("FZ","FX",samplesheet$art)
groups <- factor(samplesheet$art,levels=c("NAT","FX"))
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_nat_vs_fx <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fx",
    myann=myann, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="IUI" | art=="FH" | art=="FZ")
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
samplesheet$art <- gsub("FH","FX",samplesheet$art)
samplesheet$art <- gsub("FZ","FX",samplesheet$art)
groups <- factor(samplesheet$art,levels=c("IUI","FX"))
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_iui_vs_fx <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_iui_vs_fx",
    myann=myann, beta=beta_flt)

>>>>

top_nat_vs_fh_inc <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval,name="top_nat_vs_fh_inc",
    myann=anno ,beta= beta)

@@

top_nat_vs_fh <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fh",
    myann=anno, beta=beta_flt)

@@

top_nat_vs_fz <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fz",
    myann=anno, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="NAT" | art=="IUI")
groups <- factor(samplesheet$art,levels=c("NAT","IUI"))
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_nat_vs_iui <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_iui",
    myann=anno, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="FH" | art=="FZ")
groups <- factor(samplesheet$art,levels=c("FH","FZ"))
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_fh_vs_fz <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_fh_vs_fz",
    myann=anno, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="NAT" | art=="FH" | art=="FZ")
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
samplesheet$art <- gsub("FH","FX",samplesheet$art)
samplesheet$art <- gsub("FZ","FX",samplesheet$art)
groups <- factor(samplesheet$art,levels=c("NAT","FX"))
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_nat_vs_fx <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_nat_vs_fx",
    myann=anno, beta=beta_flt)

@@

samplesheet <- subset(targets,art=="IUI" | art=="FH" | art=="FZ")
samplesheet$Basename <- sapply(strsplit(samplesheet$Basename, "/"), "[[", 3)
samplesheet$art <- gsub("FH","FX",samplesheet$art)
samplesheet$art <- gsub("FZ","FX",samplesheet$art)
groups <- factor(samplesheet$art,levels=c("IUI","FX"))
sex <- factor(samplesheet$sex,levels=c("Male","Female"))
table(groups)
top_iui_vs_fx <- dm_analysis(samplesheet=samplesheet,
    sex=sex,groups=groups,mx=Mval_flt,name="top_iui_vs_fx",
    myann=anno, beta=beta_flt)
